---
title       : Practical learning machine
subtitle    : Assignment Writeup - Prediction of how was Exercise Performed -
author      : Carlos Pinilla
job         :
logo        :
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow   #
url:
  lib: ../../librariesNew
  assets: ../../assets
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---
 
 
```{r setup, cache = F, echo = F, message = F, warning = F, tidy = F}
library(knitr); library(caret); library(randomForest)
# make this an external chunk that can be included in any file
options(width = 100)
opts_chunk$set(message = F, error = F, warning = F, comment = NA, fig.align = 'center', dpi = 100, tidy = F, cache.path = '.cache/', fig.path = 'fig/')
 
options(xtable.type = 'html')
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)) {
    round(x, getOption('digits'))
  } else {
    paste(as.character(x), collapse = ', ')
  }
})
knit_hooks$set(plot = knitr:::hook_plot_html)
```
 
 
## Introduction
 
As nowdays we count with a large quantity of wereables, it is easy to collect a big amount of data relative to Human Activity Recognition. We count with a dataset with information about accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways and the goal is to use data to predict the exercises did by the volunters based in the data registered.
 
## Data
 
The training data for this project was taken from:
 
[https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv)
 
The test data was taken from:
 
[https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv)
 
The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har.
 
---
 
## Getting the data
 
```{r loadData,cache=TRUE}
library(ggplot2); library(caret);library(RCurl)
# Download data.
dir_data_training <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
file_data_training <- "pml-training.csv"
download.file(url=dir_data_training, destfile=file_data_training)
dir_data_testing <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
file_data_testing <- "pml-testing.csv"
download.file(url=dir_data_testing, destfile=file_data_testing)
 
# Import the data treating empty values as NA.
training <- read.csv(file_data_training, na.strings=c("NA",""), header=TRUE)
colnames_train <- colnames(training)
testing <- read.csv(file_data_testing, na.strings=c("NA",""), header=TRUE)
colnames_test <- colnames(testing)
dim(training)
dim(testing)
```
 
 
 
---
 
## Get training/test sets
 
```{r trainingTest,dependson="loadData",cache=TRUE}

na_test = sapply(training, function(x) {sum(is.na(x))})
table(na_test)

bad_columns = names(na_test[na_test==19216])
training1 = training[, !names(training) %in% bad_columns]
str(training)


SubTrain <- createDataPartition(y=training1$classe,p=0.6, list=FALSE)
Subtraining <- training1[SubTrain,]; Subtesting <- training1[-SubTrain,]
dim(Subtraining); dim(Subtesting)

```
 
 
 
 
---

## Random forests

I decided to use the Random Forest method because I am interested in the accuracy and have enought time to train my learning machine.

```{r fig.height=4,fig.width=4,cache=TRUE}
modFit <- train(classe~ .,data=Subtraining,method="rf",prox=TRUE)
modFit

```

---

## Getting a single tree

```{r , dependson="forestIris",fig.height=4,fig.width=4}
getTree(modFit$finalModel,k=2)
```

---

## Class "centers"

```{r centers, dependson="forestIris",fig.height=4,fig.width=4}
irisP <- classCenter(Subtraining[,c(55,56)], Subtraining$Classe, modFit$finalModel$prox)
irisP <- as.data.frame(irisP); irisP$classe <- rownames(irisP)
p <- qplot(accel_forearm_y, accel_forearm_z, col=classe,data=Subtraining)
p + geom_point(aes(x=accel_forearm_y,y=accel_forearm_z,col=classe),size=5,shape=4,data=Subtraining)
```

---

## Predicting new values

```{r predForest, dependson="centers",fig.height=4,fig.width=4,cache=TRUE}
pred <- predict(modFit,Subtesting); Subtesting$predRight <- pred==Subtesting$classe
table(pred,Subtesting$classe)
```

---

## Predicting new values

```{r, dependson="predForest",fig.height=4,fig.width=4}
##qplot(Petal.Width,Petal.Length,colour=predRight,data=testing,main="newdata Predictions")
```

---